### 2017-03-02 Lab_4/solutions/L4-2-1.tex

in de eerdere kreeg authentication als reply succesful, nu is het unspecified failure
<pkt ids>

>>>>

In the first dump, when the station sent an authentication frame (pkt ID 2666) it was
followed by an authentication frame (pkt ID 2668) indicating the succesful authentication
of STA with AP in the WLAN management frame status code.\\
In the second case, with mac filtering enabled and configured to not allow STA1's wlan0 to connect,
the authentication frame(pkt ID 464) sent by STA1 is met with an authentication frame(pkt ID 466) sent by the AP
with a status code 0x0001 signalling an unspecified failure which prevents the establishment of STA's connection with AP.
in de eerdere kreeg authentication als reply succesful, nu is het unspecified failure
<pkt ids>
